Vegetation Change Assessment - SOD Plots in Sonoma County

### 2016-02-25 veg-change-assessment.Rmd
Rename data frames.

```{r load overstory tree data, echo=F, results='hide', message=FALSE}
# Tagged Stems
stems <- as.tbl(read.csv("analysis/data/stems_noBUSH01.csv"))
stems
stems$plotid <- tolower(stems$plotid)
stems$species <- tolower(stems$species)

# Overstory species data of tagged and untagged stems
tag_dbh_plot <- as.tbl(read.csv("analysis/data/tag-dbh-plot.csv"))
tag_dbh_plot
tag_dbh_plot$plotid <- tolower(tag_dbh_plot$plotid)
tag_dbh_plot$species <- tolower(tag_dbh_plot$species)
tag_dbh_stem <- as.tbl(read.csv("analysis/data/tag-dbh_0514-corrected.csv"))
tag_dbh_stem
tag_dbh_stem$plotid <- tolower(tag_dbh_stem$plotid)
tag_dbh_stem$species <- tolower(tag_dbh_stem$species)
alt_dbh_plot <- as.tbl(read.csv("analysis/data/alt-dbh-plot.csv"))
alt_dbh_plot
alt_dbh_stem <- as.tbl(read.csv("analysis/data/alt-species-dbh-corrected.csv"))
alt_dbh_stem

dbh_stem <- rbind(select(tag_dbh_stem, plotid, species, dbh, status, year),
                  alt_dbh_stem)
dbh_stem$plotid <- as.factor(dbh_stem$plotid)
dbh_stem$status <- as.factor(dbh_stem$plotid)
dbh_stem$year <- as.factor(dbh_stem$year)

>>>>

```{r load overstory tree data, echo=F, results='hide', message=FALSE}
# Tagged Stems
tagged_stems <- as.tbl(read.csv("analysis/data/tagged-stems-corrected.csv"))
tagged_stems
tagged_stems$plotid <- tolower(tagged_stems$plotid)
tagged_stems$species <- tolower(tagged_stems$species)

# Overstory species data of tagged and untagged stems
tag_dbh_plot <- as.tbl(read.csv("analysis/data/tag-dbh-plot.csv"))
tag_dbh_plot
tag_dbh_plot$plotid <- tolower(tag_dbh_plot$plotid)
tag_dbh_plot$species <- tolower(tag_dbh_plot$species)

tag_dbh_stem <- as.tbl(read.csv("analysis/data/tag-dbh_0514-corrected.csv"))
tag_dbh_stem
tag_dbh_stem$plotid <- tolower(tag_dbh_stem$plotid)
tag_dbh_stem$species <- tolower(tag_dbh_stem$species)

alt_dbh_plot <- as.tbl(read.csv("analysis/data/alt-dbh-plot.csv"))
alt_dbh_plot

alt_dbh_stem <- as.tbl(read.csv("analysis/data/alt-species-dbh-corrected.csv"))
alt_dbh_stem

all_stems <- as.tbl(read.csv("analysis/data/all_stems_corrected.csv"))
summary(all_stems)
      # rbind(select(tag_dbh_stem, plotid, species, dbh, status, year),
      #             alt_dbh_stem)
all_stems$plotid <- as.factor(all_stems$plotid)
all_stems$status <- as.factor(all_stems$plotid)
all_stems$year <- as.factor(all_stems$year)
